### 2024-03-15 sections/2homology.tex
ignore this for the moment

We will now recall the $\infty$-category of disk algebras with a chosen tangential structure valued in a symmetric monoidal $\infty$-category. First, recall Segal's category $\mathsf{Fin}_{\ast}$ of finite pointed sets and their maps. By abuse, we write $\mathsf{Fin}_\ast=\mathsf{N}(\mathsf{Fin}_\ast)$ for its nerve. Following \cite{lurie_ha}, we take the objects of $\mathsf{Fin}_{\ast}$ to be $\langle n\rangle=\{\ast,1,\dots,n\}$. For every $i\in\{1,\dots,n\}$ there is a map $\rho^i\colon\langle n\rangle\to\langle 1\rangle$ that sends $i$ to $1$ but is otherwise constant at $\ast\in\langle1\rangle$. A \emph{symmetric monoidal $\infty$-category} is, according to \cite[Definition 2.0.0.7]{lurie_ha}, a cocartesian fibration\footnote{A \emph{cocartesian fibration} (\cite[Definition 01T5]{lurie_kerodon}) $q\colon\mathscr{A}\to\mathscr{B}$ between simplicial sets is one such that every edge $f\colon\mathscr{A}_1$ is \emph{$q$-cocartesian}, that is, any horn of type $\Lambda^n_0\to\mathscr{A}$, $n\geq2$, whose restriction to $\{0<1\}$ is $f$, admits a filler if its projection to $\mathscr{B}$ admits a filler.} $\catC\to\mathsf{Fin}_\ast$ such that the maps the maps $\rho^i\colon\langle n\rangle\to\langle 1\rangle$, $1\leq i\leq n$, induce an equivalence $\catC_{\langle n\rangle}\simeq(\catC_{\langle 1\rangle})^{\times n}$ for every $n\geq0$, where $\catC_{x}$ is the fiber at $x$. We mostly abbreviate $\catC\to\mathsf{Fin}_\ast$ to $\catC$.

The $\infty$-category $\mathsf{Fun}^{\otimes}(\catC,\mathscr{D})\subset\mathsf{Fun}_{/\mathsf{Fun}_\ast}(\catC,\mathscr{D})$ of \emph{symmetric monoidal functors} is the full sub-$\infty$-category of all the functor $\infty$-category on those functors that preserve cocartesian edges.

>>>>

We will now recall the $\infty$-category of disk algebras with a chosen tangential structure valued in a symmetric monoidal $\infty$-category. First, consider, following \cite{lurie_ha}, the category $\mathsf{Fin}_\ast$ whose objects are the sets $\langle n\rangle=\{\ast,1,\dots,n\}$ and whose morphisms are functions that preserve the distinguished point $\ast$. For every $i\in\{1,\dots,n\}$ there is a map $\rho^i\colon\langle n\rangle\to\langle 1\rangle$ that sends $i$ to $1$ but is otherwise constant at $\ast\in\langle1\rangle$. A \emph{symmetric monoidal $\infty$-category} is, after \cite[Definition 2.0.0.7]{lurie_ha}, a cocartesian fibration\footnote{A \emph{cocartesian fibration} (\cite[Definition 01T5]{lurie_kerodon}) $q\colon\mathscr{A}\to\mathscr{B}$ between simplicial sets is one such that every edge $f\in\mathscr{A}_1$ is \emph{($q$-)cocartesian}, that is, any horn of type $\Lambda^n_0\to\mathscr{A}$, $n\geq2$, whose restriction to $\{0<1\}$ is $f$, admits a filler if its projection to $\mathscr{B}$ admits a filler. By (un)straightening, such a $q$ corresponds to a $\cat$-valued copresheaf $\mathscr{B}\to\cat$.} $\catC\to\mathsf{Fin}_\ast$ such that the maps $\rho^i\colon\langle n\rangle\to\langle 1\rangle$, $1\leq i\leq n$, induce an equivalence $\catC_{\langle n\rangle}\simeq(\catC_{\langle 1\rangle})^{\times n}$ for every $n\geq0$, where $\catC_{x}$ is the fiber at $x$. We have abbreviated $\mathsf{N}(\mathsf{Fin}_\ast)$ to $\mathsf{Fin}_\ast$, and will mostly abbreviate $\catC\to\mathsf{Fin}_\ast$ to $\catC$.

The $\infty$-category $\mathsf{Fun}^{\otimes}(\mathscr{O},\catC)\subset\mathsf{Fun}_{/\mathsf{Fin}_\ast}(\mathscr{O},\catC)$ of \emph{symmetric monoidal functors} between symmetric monoidal $\infty$-categories $\mathscr{O}$, $\catC$ is the full sub-$\infty$-category of the $\infty$-category of functors over $\mathsf{Fin}_\ast$ generated by those functors that preserve cocartesian edges. Following \cite{aft_fhstrat}, we write 
\[
    \alg{\mathscr{O}}(\mathscr{C})\coloneqq\mathsf{Fun}^{\otimes}(\mathscr{O},\mathscr{C})
\]
when $\mathscr{O}$, $\mathscr{C}$ are symmetric monoidal $\infty$-categories.

More generally, an \emph{$\infty$-operad}, after \cite{lurie_ha}, is a map $\mathscr{C}\to\mathsf{Fin}_\ast$ which is only required to be a cocartesian fibration upon restricting to $\mathsf{Fin}_{\ast}^{\text{inrt}}\subset\mathsf{Fin}_\ast$, the subcategory of \emph{inert} morphisms $f\colon\langle m\rangle\to \langle n\rangle$ for which, by definition, $f^{-1}\{i\}$ is a singleton whenever $i\in\langle n\rangle^{\circ}\coloneqq\{1,\dots,n\}\subset\langle n\rangle$.
